Pool Model Paper

### 2023-08-11 pool_model.tex
add LV examples/references

which has the structure of a generalised Lotka-Volterra system. \cmt{Add reference about Lotka-Volterra. Compare with different states LV.}
In order to better see this, we set $L_A=L_B=0$: 
\begin{eqnarray}
\label{Comp_Model}
\dot{G}_A &=& \alpha_A G_A\left(1 - \frac{G_A}{N_t}\right ) - \frac{\alpha_A}{N_t}G_AG_B\\
\dot{G}_B &=& \alpha_B G_B\left(1-\frac{G_B}{N_t}\right ) -\frac{\alpha_B}{N_t}G_AG_B. 
\label{eq:LV_simple}
\end{eqnarray}

Equations (\ref{eq:LV_simple}) are basically competitive Lotka-Volterra equations that are widely used in ecological studies and show the principle of competive excursion.
That principle claims that two species in competition for the same resource cannot coexist~\cite{wangersky_lotka-volterra_1978}.

>>>>

which has the structure of a generalised Lotka-Volterra system (gLV). \cmt{Add reference about Lotka-Volterra. Compare with different states LV.}
In order to better see this, we set $L_A=L_B=0$: 
\begin{eqnarray}
\label{Comp_Model}
\dot{G}_A &=& \alpha_A G_A\left(1 - \frac{G_A}{N_t}\right ) - \frac{\alpha_A}{N_t}G_AG_B\\
\dot{G}_B &=& \alpha_B G_B\left(1-\frac{G_B}{N_t}\right ) -\frac{\alpha_B}{N_t}G_AG_B. 
\label{eq:LV_simple}
\end{eqnarray}

Equations (\ref{eq:LV_simple}) are basically competitive Lotka-Volterra equations that are widely used in ecological studies and show the principle of competive excursion.
That principle claims that two species in competition for the same resource cannot coexist~\cite{wangersky_lotka-volterra_1978}. 
In previous studies it was shown that gLV equations can be sucessfully applied to predict the microbial community dynamics, determine different types of the pairwise interspecies interactions~\cite{dedrick_when_2023, stein_ecological_2013, venturelli_deciphering_2018, hoffmann_power_2007}.
In food studies the gLV was applied by Mounier \etal~\cite{mounier_microbial_2008} to study interactions of 6 bacteria species  with yeast omissin in cheese.
